---
title: "Lab 00 - Hello IDS!"
author: "Robert-John Bryce"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Harry", "Greg", 
           "Robert", "Roderick"),
  github_username = c("mcgregors-garden", "HarryFerguson08", "username 2", 
                      "DuckBio", "roryyu16-ops"), 
  colour = c("powderblue", "green", "blue", 
             "purple", "blue"),
  hobby = c("Hopping", "rugby", "hobby 2", 
            "reading", "Video Games"),
  favourite_number = c(2, 1, 5, 7, 8)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

It shows the peoples usernames, their favourite number and the bar shows their favourite colours.


### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Insert text here", 
          y = "Insert text here",
          title = "Insert text here")
```

It is used to modify the labels of the plot, inlcuding the axes and the legend.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

It would be messy to visualise so many different answers, especially since the variety would result in little cases of the same answer. Instead of counting them, one should display each hobby individually.
